data_cleaning_longer_period

### 2024-08-26 code/manuscript_analysis.Rmd
stick to the original sample, just reconfigure visuals to tell story

dfc %>% 
  filter(Year == 2010) %>% 
  mutate(Treat = ifelse(Att > 0, "Treated", "Control")) %>% 
  select(Treat, Total, Pct.NHA:Pct.COM) %>% 
  #filter(!complete.cases(.)) %>% 
  tbl_summary(by = Treat, 
                statistic = list(all_continuous() ~ "{mean} ({sd})"),
missing = "no", digits = list(everything() ~ c(2))) %>% 
  add_p(pvalue_fun = function(x) style_pvalue(x, digits = 3))

@@

plot0 <- p %>% 
  arrange(CompetitorsInArea) %>% 
  ggplot(aes(x = Year, y = Count, group = CompetitorsInArea, color = CompetitorsInArea)) + ylab("FQHCs") + 
  geom_point(size = 1.1) + geom_line(size = 1.1) + theme_tufte_revised() + ggtitle("FQHCs by Number of Colocated FQHCs") + 
  geom_dl(label=c(rep("0 Competitors", 25), rep("1 Competitor", 25), rep("2 Competitors", 25), rep("3+ Competitors", 25)), 
          method = list("last.points", hjust = 1, vjust = c(3, 3.5, 4, -2), cex = 1.5), inherit.aes=T ) + 
  guides(colour = "none") +theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

plot1 <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
            group_by(Zip, Year) %>% 
  summarise(Counts = n()) %>% 
  #summarise(Counts = n_distinct(`Grant Number`)) %>% 
  ungroup() %>% 
  group_by(Year, Counts) %>% 
  summarise(Zips = n()) %>% 
  mutate(Counts.f = as.factor(ifelse(Counts >= 2, "2+", Counts))) %>% 
  group_by(Counts.f, Year) %>% 
  summarise(Zips = sum(Zips)) %>% 
  #filter(Year >= 2010) %>% 
  ggplot(aes(x = Year, y = Zips, group = Counts.f, color = Counts.f)) + 
  geom_point(size = 1.1) + geom_line(size = 1.1) + theme_tufte_revised() + ggtitle("Zip Codes by Number of FQHC Sites") + 
  geom_dl(label=c(rep("1 Site", 25), rep("2+ Sites", 25)), method = list("last.points", hjust = 1, vjust = -1, cex = 1.5), inherit.aes=T ) + 
  guides(colour = "none") + ylim(0, 4000) +theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

@@

p.desc
```

@@

ggsave(filename = "Picture14.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p14, width = 17, height = 9)

@@

ggsave(filename = "Picture4.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p2, width = 17, height = 9)

@@

## Read in Centroid Data
zip.centroids <- read.csv("/Users/jhm65/Dropbox/Git/Data/ZIP_Code_Population_Weighted_Centroids.csv") %>% 
  mutate(ZipCode = str_pad(STD_ZIP5, 5, pad = "0")) %>% 
  select(ZipCode, X, Y)
## Add missing centroids
zip.centroids <- rbind(zip.centroids, c(ZipCode = "37243", X = -86.783, Y = 36.165), 
                                      c(ZipCode = "95951", X = -121.98, Y = 39.73), 
                                      c(ZipCode = "99733", X = -144.166941, Y = 65.799773)) %>% 
  mutate(X = as.numeric(X), Y = as.numeric(Y))

@@

## Rival selecting where to put new site, takes 30+ minutes to work

>>>>

dfc %>% 
  filter(Year == 2011) %>% 
  mutate(Treat = ifelse(Att > 0, "Treated", "Control")) %>% 
  select(Treat, Total, Pct.NHA:Pct.COM) %>% 
  #filter(!complete.cases(.)) %>% 
  tbl_summary(by = Treat, 
                statistic = list(all_continuous() ~ "{mean} ({sd})"),
missing = "no", digits = list(everything() ~ c(2))) %>% 
  add_p(pvalue_fun = function(x) style_pvalue(x, digits = 3))

@@

plot0 <- p %>% 
  arrange(CompetitorsInArea) %>% 
  ggplot(aes(x = Year, y = Count, group = CompetitorsInArea, color = CompetitorsInArea)) + ylab("FQHCs") + 
  geom_point(size = 1.1) + geom_line(size = 1.1) + theme_tufte_revised() + ggtitle("FQHCs by Number of Colocated FQHCs") + 
  geom_dl(label=c(rep("0 Competitors", length(unique(p$Year))), rep("1 Competitor", length(unique(p$Year))), rep("2 Competitors", length(unique(p$Year))), rep("3+ Competitors", length(unique(p$Year)))), 
          method = list("last.points", hjust = 1, vjust = c(3, 3.5, 4, -2), cex = 1.5), inherit.aes=T ) + 
  guides(colour = "none") +theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

plot1 <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
            group_by(Zip, Year) %>% 
  summarise(Counts = n()) %>% 
  #summarise(Counts = n_distinct(`Grant Number`)) %>% 
  ungroup() %>% 
  group_by(Year, Counts) %>% 
  summarise(Zips = n()) %>% 
  mutate(Counts.f = as.factor(ifelse(Counts >= 2, "2+", Counts))) %>% 
  group_by(Counts.f, Year) %>% 
  summarise(Zips = sum(Zips)) %>% 
  #filter(Year >= 2010) %>% 
  ggplot(aes(x = Year, y = Zips, group = Counts.f, color = Counts.f)) + 
  geom_point(size = 1.1) + geom_line(size = 1.1) + theme_tufte_revised() + ggtitle("Zip Codes by Number of FQHC Sites") + 
  geom_dl(label=c(rep("1 Site", length(unique(p$Year))), rep("2+ Sites", length(unique(p$Year)))), method = list("last.points", hjust = 1, vjust = -1, cex = 1.5), inherit.aes=T ) + 
  guides(colour = "none") + ylim(0, 4000) +theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

@@

p.desc

@@

#ggsave(filename = "Picture14.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p14, width = 17, height = 9)

@@

#ggsave(filename = "Picture4.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p2, width = 17, height = 9)

@@

## Read in Centroid Data
zip.centroids <- read.csv("/Users/markow/Dropbox/Git/Data/ZIP_Code_Population_Weighted_Centroids.csv") %>% 
  mutate(ZipCode = str_pad(STD_ZIP5, 5, pad = "0")) %>% 
  select(ZipCode, X, Y)
## Add missing centroids
zip.centroids <- rbind(zip.centroids, c(ZipCode = "37243", X = -86.783, Y = 36.165), 
                                      c(ZipCode = "95951", X = -121.98, Y = 39.73), 
                                      c(ZipCode = "99733", X = -144.166941, Y = 65.799773)) %>% 
  mutate(X = as.numeric(X), Y = as.numeric(Y))

@@

## Rival selecting where to put new site, takes 15+ minutes to work

### 2024-08-26 code/manuscript_data_cleaning.Rmd
stick to the original sample, just reconfigure visuals to tell story

@@

# Identify clinics in competitive zip codes
clinics.comp <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
  filter(Year >= included.years[1]) %>%
  select(`BHCMIS ID`, Zip, Year) %>% 
  unique() %>% 
  left_join(clinics.in.zips, by = c("Zip", "Year")) %>% 
  group_by(`BHCMIS ID`, Year) %>% 
  summarise(Clinics = max(Clinics)) %>% 
  pivot_wider(id_cols = `BHCMIS ID`, names_from = Year, values_from = Clinics) %>% 
  filter(`2010` == 1 & `2011` == 1) %>%  #  & `2012` == 1 & `2013` == 1 & `2014` == 1 & `2015` == 1 & `2016` == 1) %>%   
  #filter(`2014` == 1 & `2015` == 1) %>%  
  #left_join(chc.term, by = c("BHCMIS ID" = "ClinicID")) %>%
  #filter(is.na(NewClinicID)) %>%
  select(`BHCMIS ID`:`2021`) %>% 
  pivot_longer(cols = c(`2010`:`2021`)) %>% 
  group_by(`BHCMIS ID`) %>% 
  filter(min(value) == 1 ) %>% 
  #filter(max(value) == last(value)) %>% 
  mutate(Tx = ifelse(value > 1, 1, 0))

# Classify clinics by introduction of competition
comp.initial <- clinics.comp %>%  #left_join(clinics.comp %>% mutate(Year = as.numeric(name)), uds.zip.totals, by = c("BHCMIS ID", "name" = "Reporting Year")) %>% 
  mutate(Year = as.numeric(name)) %>% 
  left_join(uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
              filter(Year >= included.years[1]) %>%
  group_by(`BHCMIS ID`, Year) %>% 
  summarise(Sites = n()), by = c("BHCMIS ID","Year")) %>% 
  ungroup() %>% 
  group_by(`BHCMIS ID`) %>% 
  mutate(Att = min(ifelse(Tx == 0, 2, 1)*Year, na.rm = TRUE) ) %>% 
  group_by(`BHCMIS ID`) %>% 
  mutate(Att = ifelse(Att < 2024, Att, 0)) %>% 
  ungroup() %>% 
  mutate(ID = as.numeric(factor(`BHCMIS ID`)))

# Expandors vs Expandees
comp.initial <- comp.initial %>% 
  left_join(
      left_join(comp.initial %>% select(`BHCMIS ID`, Att) %>% unique(), uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
                  filter(Year >= included.years[1]) %>%
        select(`BHCMIS ID`, Zip, Year) %>% 
        group_by(`BHCMIS ID`, Zip) %>% 
        summarise(YearFirstInZip = min(Year)) %>% 
        filter(YearFirstInZip %notin% c(2010)) %>% 
        select(`BHCMIS ID`, YearFirstInZip) %>% 
        unique(), by = c("BHCMIS ID")) %>% #filter(`BHCMIS ID` == "H80CS00101") %>% 
        mutate(Expandor = ifelse(is.na(YearFirstInZip) | Att != YearFirstInZip, 0, 1)) %>%  #  is.na(YearFirstInZip) | Att != YearFirstInZip
        group_by(`BHCMIS ID`) %>% summarise(Expandor = max(Expandor)), by = c("BHCMIS ID"))

@@

vec.atts <- rep(c(2012:2021), (table(comp.initial$Att) / 12)[-1])

@@

## Write the file
```{r}
# write_csv(dfc, file = "/Users/markow/Dropbox/Git/Competition/data_processed/manuscript_analyticalfile.csv")
# write.csv(uds.sites.full, file = "/Users/markow/Dropbox/Git/Competition/data_processed/manuscript_sites_geocoded.csv")
```

>>>>

 included.years <- 2014:2023
 included.treat <- 2016:2023

@@

# Identify clinics in competitive zip codes
clinics.comp <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
  filter(Year >= included.years[1]) %>%
  select(`BHCMIS ID`, Zip, Year) %>% 
  unique() %>% 
  left_join(clinics.in.zips, by = c("Zip", "Year")) %>% 
  group_by(`BHCMIS ID`, Year) %>% 
  summarise(Clinics = max(Clinics)) %>% 
  pivot_wider(id_cols = `BHCMIS ID`, names_from = Year, values_from = Clinics) %>% 
  #filter(`2011` == 1 & `2012` == 1 ) %>%  #  & `2012` == 1 & `2013` == 1 & `2014` == 1 & `2015` == 1 & `2016` == 1) %>%   
  filter(`2014` == 1 & `2015` == 1) %>%  
  #left_join(chc.term, by = c("BHCMIS ID" = "ClinicID")) %>%
  #filter(is.na(NewClinicID)) %>%
  select(`BHCMIS ID`:`2023`) %>% 
  pivot_longer(cols = c(`2014`:`2023`)) %>% 
  group_by(`BHCMIS ID`) %>% 
  filter(min(value) == 1 ) %>% 
  #filter(max(value) == last(value)) %>% 
  mutate(Tx = ifelse(value > 1, 1, 0))

# Classify clinics by introduction of competition
comp.initial <- clinics.comp %>%  #left_join(clinics.comp %>% mutate(Year = as.numeric(name)), uds.zip.totals, by = c("BHCMIS ID", "name" = "Reporting Year")) %>% 
  mutate(Year = as.numeric(name)) %>% 
  left_join(uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
              filter(Year >= included.years[1]) %>%
  group_by(`BHCMIS ID`, Year) %>% 
  summarise(Sites = n()), by = c("BHCMIS ID","Year")) %>% 
  ungroup() %>% 
  group_by(`BHCMIS ID`) %>% 
  mutate(Att = min(ifelse(Tx == 0, 2, 1)*Year, na.rm = TRUE) ) %>% 
  group_by(`BHCMIS ID`) %>% 
  mutate(Att = ifelse(Att < max(included.treat)+1, Att, 0)) %>% 
  ungroup() %>% 
  mutate(ID = as.numeric(factor(`BHCMIS ID`)))

# Expandors vs Expandees
comp.initial <- comp.initial %>% 
  left_join(
      left_join(comp.initial %>% select(`BHCMIS ID`, Att) %>% unique(), uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
                  filter(Year >= included.years[1]) %>%
        select(`BHCMIS ID`, Zip, Year) %>% 
        group_by(`BHCMIS ID`, Zip) %>% 
        summarise(YearFirstInZip = min(Year)) %>% 
        filter(YearFirstInZip %notin% min(included.years)) %>% 
        select(`BHCMIS ID`, YearFirstInZip) %>% 
        unique(), by = c("BHCMIS ID")) %>% #filter(`BHCMIS ID` == "H80CS00101") %>% 
        mutate(Expandor = ifelse(is.na(YearFirstInZip) | Att != YearFirstInZip, 0, 1)) %>%  #  is.na(YearFirstInZip) | Att != YearFirstInZip
        group_by(`BHCMIS ID`) %>% summarise(Expandor = max(Expandor)), by = c("BHCMIS ID"))

@@

vec.atts <- rep(included.treat, (table(comp.initial$Att) / 12)[-1])

@@

## Write the file
```{r}
# write_csv(dfc, file = "/Users/markow/Dropbox/Git/Competition/data_processed/manuscript_analyticalfile.csv")
# write.csv(uds.sites.full, file = "/Users/markow/Dropbox/Git/Competition/data_processed/manuscript_sites_geocoded.csv")
